---
title: "R-Ladies Helsinki February Event"
author: "Hazel KAVILI"
date: "1/27/2020"
output: pdf_document
---

## Spotify Songs
We will work on a *[TidyTuesday](https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-01-21/readme.md)* dataset today. 
*(Try to check out the TidyTuesday concept after the event! You'll love it!)*

#### Load libraries 
```{r error = FALSE, warning=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(knitr)
library(kableExtra)
```

#### Read the data set from source
```{r message=FALSE}
spotify_songs <- 
  readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-01-21/spotify_songs.csv')
```

#### Start Exploring
*glimpse* function makes it possible to see every column and some observations in a data frame. 
```{r}
glimpse(spotify_songs)
```

#### Exploring data
Some songs are duplicated, because they're in different albums or in different playlist. I wonder, how many distinct tracks there are for each artist:

```{r}
artists_tracks <- spotify_songs %>% 
  distinct(track_id, .keep_all = TRUE) %>% 
  count(track_artist, sort = TRUE) %>%
  top_n(n = 20, wt = n)
```

A stylish table:
```{r}
head(artists_tracks) %>% 
  kable(align = "lccrr",  caption = "Top 10 artists with most tracks")
```

Let's create a plot by using this data:
```{r}
artist_plot <- ggplot(data = artists_tracks, aes(x = reorder(track_artist, n), y = n)) +
  geom_bar(stat = 'identity') +
  coord_flip() +
  labs(title = 'Top 20 artists with most tracks in list', 
       x = 'Artists', 
       y = 'Number of tracks')

artist_plot
```










